The Construction of Set-Truncated Higher Inductive Types

### 2019-05-01 paper/paper.tex
Added reference, fixed typos

\usepackage{cleveref}
\usepackage{entcsmacro}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{bussproofs}
\usepackage{stmaryrd}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{coq}
\usepackage{color}
\usepackage{xcolor}
\usepackage[all]{xy}

@@

\subsection{The Adjunction on Prealgebras}
With this adjunction in place, our first step is to lift it to the level of prealgebras.
The first step, is to lift the functors for which we use the following lemma.

@@

\begin{proposition}
\label{lem:prealgadjconstr}
Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_1 : \functor{\mathcal{C}}{\mathcal{C}}$, $A_2 : \functor{\mathcal{D}}{\mathcal{D}}$, and $L : \functor{\mathcal{C}}{\mathcal{D}}$, and a natural transformation $n : \nattrans{\compf{L}{A_2}}{\compf{A_1}{L}}$.
In addition, suppose we a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{L}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
We also assume that for each $X : \mathcal{C}$ and $Y : \mathcal{D}$ the following diagrams commute
\[
\xymatrix
{	
	A_2 (L(R \> X)) \ar[ddrr]^{\epsilon \> X} \ar[d]_{n(R \> X)} \\
	L(A_2(R \> X)) \ar[d]_{L(m \> X} \\
	R(L(A_2 \> X)) \ar[rr]_-{\epsilon(A_2 \> X)} & & A_2 \> X
}
\quad \quad \quad
\xymatrix
{
	A_1 \> Y \ar[ddrr]_{\eta \> (A_1 \> X)} \ar[rr]^-{A_1 \> (\eta \> Y)} & & A_1(R(L \> Y)) \ar[d]^{m(L \> X)}\\
	& & R(A_1(L \> X)) \ar[d]^{R(n \> X)}\\
	& & R(L(A_1 \> Y))
}
\]
Then the maps $\varepsilon \> X$ and $\eta \> Y$ are algebra homomorphisms for each $X : \mathcal{C}$ and $Y : \mathcal{D}$.
Furthermore, we have an adjunction $\adj{L^{\category{PreAlg}}}{R^{\category{PreAlg}}}$.
\end{proposition}

@@

>>>>

\usepackage{entcsmacro}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{bussproofs}
\usepackage{stmaryrd}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{coq}
\usepackage{color}
\usepackage{xcolor}
\usepackage[all]{xy}

@@

\subsection{The Adjunction on Prealgebras}
With this adjunction in place, our first step is to lift it to the level of prealgebras.
For this, we use a result from Hermida and Jacobs \cite{hermida1998structural}.
The first step, is to lift the functors for which we use the following lemma.

@@

\begin{proposition}
\label{lem:prealgadjconstr}
Given are categories $\mathcal{C}$ and $\mathcal{D}$, functors $A_1 : \functor{\mathcal{C}}{\mathcal{C}}$, $A_2 : \functor{\mathcal{D}}{\mathcal{D}}$, and $L : \functor{\mathcal{C}}{\mathcal{D}}$, and a natural transformation $n : \nattrans{\compf{L}{A_2}}{\compf{A_1}{L}}$.
In addition, suppose we a functor $R : \functor{\mathcal{D}}{\mathcal{C}}$ together with a natural transformation $m : \nattrans{\compf{R}{A_1}}{\compf{A_2}{R}}$ and an adjunction $\adj{L}{R}$ with unit $\eta$ and counit $\varepsilon$.
We also assume that for each $X : \mathcal{C}$ and $Y : \mathcal{D}$ the following diagrams commute
\[
\xymatrix
{	
	A_2 (L(R \> X)) \ar[ddrr]^{\epsilon \> X} \ar[d]_{n(R \> X)} \\
	L(A_2(R \> X)) \ar[d]_{L(m \> X)} \\
	R(L(A_2 \> X)) \ar[rr]_-{\epsilon(A_2 \> X)} & & A_2 \> X
}
\quad \quad \quad
\xymatrix
{
	A_1 \> Y \ar[ddrr]_{\eta \> (A_1 \> X)} \ar[rr]^-{A_1 \> (\eta \> Y)} & & A_1(R(L \> Y)) \ar[d]^{m(L \> X)}\\
	& & R(A_1(L \> X)) \ar[d]^{R(n \> X)}\\
	& & R(L(A_1 \> Y))
}
\]
Then the maps $\varepsilon \> X$ and $\eta \> Y$ are algebra homomorphisms for each $X : \mathcal{C}$ and $Y : \mathcal{D}$.
Furthermore, we have an adjunction $\adj{L^{\category{PreAlg}}}{R^{\category{PreAlg}}}$.
\end{proposition}

@@

	\bibitem{hermida1998structural}
	C.~Hermida and B.~Jacobs.
	\newblock Structural induction and coinduction in a fibrational setting.
	\newblock {\em Information and computation}, 145(2):107--152, 1998.
